### 2010-05-04 PhysicalParameters/MooreHubbardSchwabKooijman_abstract.tex
initial commit of the abstract

%%%%%%%%%%%%%%%% authors %%%%%%%%%%%%%%%
\begin{flushleft}
  {\fontsize{12}{14}{Jason K. Moore and Mont Hubbard}\\}
  \textit{Mechanical and Aerospace Engineering\\
          University of California, Davis\\
          One Shields Avenue, Davis, CA 95616, USA\\
          e-mail: jkmoor@ucdavis.edu, mhubbard@ucdavis.edu
  }\vspace{10pt}\\
  {\fontsize{12}{14}{A. L. Schwab and J. D. G. Kooijman}\\}
  \textit{Laboratory for Engineering Mechanics\\
          Delft University of Technology, Mekelweg 2, 2628CD Delft, The
          Netherlands\\
          e-mail: a.l.schwab@tudelft.nl, jodikooijman@gmail.com
  }\vspace{10pt}\\
\end{flushleft}

@@

The moments of inertia of the rigid bodies were measured in both torsional
pendulum and compound pendulum configurations. Again the assumed symmetry of the
bicycle was utilized to reduce the number of measurements needed. The
in-symmetric-plane moments of inertia were calculated from measurements of the
rigid bodies' periods of oscillation when hung as a torsional pendulum at
different orienatation angles. The out-of-plane moments of inertia were
measured by swinging the rigid bodies as a compound pendulum.
\subsection*{Results}
Parameter sets for all six bicycles and all eight
configurations, example in Table~\ref{tab:par},  will be
presented, together with basic comparisons of the open loop dynamics of the
different types of bicycles. The physical parameters, the mass, damping and stiffness
matrices of the system, the eigenvalues and open loop transfer functions at
different speeds will be compared with typical anedoctal
descriptions of handling.
\begin{table*}[tb]
\centering
\caption{PARAMETER VALUES FOR THE BATAVUS BROWSER.}
{\small
\begin{tabular}{lcl}
&&\\
\hline
Parameter & Symbol & Value \\
\hline
wheel base & $w$ & 1.121 m \\
trail & $c$ & 0.069 m \\
steer axis tilt & \emph{$\lambda$} & 0.400 rad \\
gravity & \emph{g} & 9.81 N kg$^{-1}$ \\
forward speed & \emph{v} & various m s$^{-1}$ \\

>>>>

%%%%%%%%%%%%%%%% authors %%%%%%%%%%%%%%%
\begin{flushleft}
  {\fontsize{12}{14}{Jason K. Moore, Mont Hubbard and Dale L. Peterson}\\}
  \textit{Mechanical and Aerospace Engineering\\
          University of California, Davis\\
          One Shields Avenue, Davis, CA 95616, USA\\
          e-mail: jkmoor@ucdavis.edu, mhubbard@ucdavis.edu,
          dlpeterson@ucdavis.edu
  }\vspace{10pt}\\
  {\fontsize{12}{14}{A. L. Schwab and J. D. G. Kooijman}\\}
  \textit{Laboratory for Engineering Mechanics\\
          Delft University of Technology, Mekelweg 2, 2628CD Delft, The
          Netherlands\\
          e-mail: a.l.schwab@tudelft.nl, jodikooijman@gmail.com
  }\vspace{10pt}\\
\end{flushleft}

@@

The moments of inertia of the rigid bodies were measured in both torsional
pendulum and compound pendulum configurations. Again the assumed symmetry of the
bicycle was utilized to reduce the number of measurements needed. The
in-symmetric-plane moments of inertia were calculated from measurements of the
rigid bodies' periods of oscillation when hung as a torsional pendulum at
different orientation angles. The out-of-plane moments of inertia were
measured by swinging the rigid bodies as a compound pendulum.
\subsection*{Results}
Parameter sets for all six bicycles and all eight
configurations, example in Table~\ref{tab:par},  will be
presented, together with basic comparisons of the open loop dynamics of the
different types of bicycles. The physical parameters, the mass, damping and stiffness
matrices of the system, the eigenvalues and open loop transfer functions at
different speeds will be compared with typical anecdotal
descriptions of handling.
\begin{table*}[tb]
\centering
\caption{PARAMETER VALUES FOR THE BATAVUS BROWSER.}
{\small
\begin{tabular}{lcl}
&&\\
\hline
Parameter & Symbol & Value \\
\hline
wheel base & $w$ & 1.121 m \\
trail & $c$ & 0.069 m \\
steer axis tilt & \emph{$\lambda$} & 0.400 rad \\
gravity & \emph{g} & 9.81 N kg$^{-1}$ \\
forward speed & \emph{v} & various m s$^{-1}$ \\
